Fractional Types

### 2019-11-15 fracGC/p.tex
a bit on paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PiFrac: Generalizing Scoped Ancilla with Dynamic Checks}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Value of Ancillae}

The management of ancilla bits can be teased into two relatively
distinct subproblems:
\begin{itemize}
\item Every allocated ancilla bit must be de-allocated, and 
\item De-allocation of an ancilla bit is only safe if the bit is
  restored to its allocation-time initial value.
\end{itemize}
In this section, we focus on the first subproblem and address the
second in later sections.

%%%%%
\subsection{Scoped Ancilla}

A conventional way to ensure that every allocation is paired with a
matching de-allocation is to impose a stack discipline. An
illustrative demonstration of this idea is the \verb|with_ancilla|
operator from Quipper~\cite{Green:2013:QSQ:2491956.2462177}:
\begin{verbatim}
with_ancilla :: (Qubit -> Circ a) -> Circ a
\end{verbatim}
The operator takes a block of gates parameterized by an ancilla,
allocates a new ancilla initialized to $\ket{0}$, and runs the given
block of gates. At the end of its execution, the block is expected to
return the ancilla to the state $\ket{0}$ at which point it is
de-allocated. In this case, allocation and de-allocation of ancillae
requires nothing beyond conventional parameter-passing techniques in
which the parameter is allocated before entry to the function and
de-allocated at exit.

This scoped model is therefore quite a pragmatic choice. It is however
limited and to understand its limitations more vividly, we propose the
following analogy with money.
